|

### 2021-07-02 supplementary_information_pnas.Rmd
Update supplementary_information_pnas.Rmd

---
title: |
  ![](image/logo.png){width=4in}  
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
bibliography: reference.bib
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

@@

>>>>

---
title: |
  ![](image/logo.png){width=4in}  
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
bibliography: reference.bib
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
header-includes:
  \pagenumbering{gobble}
---

@@

\newpage
\pagenumbering{arabic}
